A framework for adaptive width control of dense contour-parallel toolpaths in additive manufacturing

### 2019-08-30 0_main.tex
cleanup abstract
Small changes by Jun and Tim
better missing includegraphics file identification

	% deal with missing images which are not directly included in the repo
	\iffalse
	\newcommand{\noimage}{%
	  \setlength{\fboxsep}{-\fboxrule}%
	  \fbox{\phantom{\rule{10pt}{10pt}}File missing\phantom{\rule{10pt}{10pt}}}% Framed box
	}
	\let\includegraphicsoriginal\includegraphics
	\renewcommand{\includegraphics}[2][width=\textwidth]{\IfFileExists{#2}{\includegraphicsoriginal[#1]{#2}}{\noimage}}
	\fi
% ENd of TK's added packages and commands

@@

\begin{abstract}
3D printing techniques such as Fused Deposition Modeling (FDM) have enabled the fabrication of complex geometry quickly and cheaply. 
By densely filling consecutive 2D layers with contour-parallel extrusion toolpaths, FDM can produce parts with high stiffness and strength.
%
Toolpath with uniform inward offsets from the outline polygons produce over- and underfill regions in the center of the shape, which are especially problematic for thin parts such as casings and microstructures. 
Some existing approaches address this issue by making local alterations to the toolpaths locations and widths in the center of the part.
%Our framework makes it possible to distribute the workload of \jun{is the sentence complete if we delete worklaod of} the alterations over larger regions farther from the center. 
In this paper we present a framework which allows to distribute the alterations from the center to the boundary.
%Based on the radial distances in the medial axis transform we decide on the number of beads and their widths from the center outward.
We present various schemes to decide the number of beads and their widths from the center outward.
%By carefully formulating various beading schemes for our framework we can emulate existing approaches.
Furthermore, we propose a novel scheme which distributes the alterations over an area large enough to avoid extremal bead width values, while limiting the number of altered toolpaths.
%
This scheme reduces the amount of over- and underfill while the extrusion widths deviate less from the nozzle size compared to existing approaches.
\end{abstract}

@@

\begin{keyword} 
Adaptive extrusion width, Tool path generation, Additive manufacturing, Geometrical accuracy, Medial axis transform, Polygon offsetting
\end{keyword}

>>>>

	% deal with missing images which are not directly included in the repo
	\iffalse
	\newcommand{\noimage}[1]{%
	  \setlength{\fboxsep}{-\fboxrule}%
	  \fbox{\phantom{\rule{10pt}{10pt}} Missing file: \path{#1} \phantom{\rule{10pt}{10pt}}}% Framed box
	}
	\let\includegraphicsoriginal\includegraphics
	\renewcommand{\includegraphics}[2][width=\textwidth]{\IfFileExists{#2}{\includegraphicsoriginal[#1]{#2}}{\noimage{#2}}}

	\fi
% ENd of TK's added packages and commands

@@

\begin{abstract}
3D printing techniques such as Fused Deposition Modeling (FDM) have enabled the fabrication of complex geometry quickly and cheaply. 
By densely filling consecutive 2D layers with contour-parallel extrusion toolpaths, FDM can produce parts with high stiffness and strength.
Toolpath with uniform inward offsets from the outline polygons produce over- and underfill regions in the center of the shape, which are especially problematic for thin parts such as casings and microstructures. 
Some existing approaches address this issue by making local alterations to the toolpaths locations and widths in the center of the part.
In this paper we present a framework which allows to distribute the alterations from the center to the boundary.
We present various schemes to decide the number of beads and their widths from the center outward.
Furthermore, we propose a novel scheme which distributes the alterations over an area large enough to avoid extremal bead width values, while limiting the number of altered toolpaths.
This scheme reduces the amount of over- and underfill while the extrusion widths deviate less from the nozzle size compared to existing approaches.
\end{abstract}

@@

\begin{keyword} 
Adaptive extrusion width, Toolpath generation, Additive manufacturing, Geometrical accuracy, Medial axis transform
\end{keyword}
